Argennon: A Scalable Cloud Based Smart Contract Platform

### 2022-08-07 tex/sections/intro.tex
typos, change PV-DB to PVC, and change confusing sentence

It appears that the only solution to this important vulnerability is to effectively participate all the stake of the
system in the consensus protocol. This large participation makes the protocol resilient against bribery or
collusion because the adversary would need to spend unrealistic amount of money to bribe enough users.

>>>>

It appears that the only solution to this important vulnerability is to effectively participate all the stake of the
system in the consensus protocol. This large participation makes the protocol resilient against bribery or
collusion because the adversary would need to spend unrealistic amounts of money to bribe enough users.
